\RequirePackage[l2tabu, orthodox]{nag}
\documentclass[letterpaper]{amsart}

\usepackage[utf8]{inputenc}
%\usepackage[T2A]{fontenc}

% MATH
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}

\usepackage[
style=alphabetic
]{biblatex}
\addbibresource{bibliography.bib}

\usepackage{hyperref}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=green,
    linkcolor=darkgray,
    urlcolor=gray
}

%\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Boris Bilich}
\address{Department of Mathematics, National Research University "Higher School of Economics",
Moscow, Russian Federation}
\email{bibilich@edu.hse.ru}
\title{Taylor spectrum for modules over Lie algebra}

\usepackage{todonotes}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{proposal}{Proposal}[theorem]
\newtheorem{corollary}{Corollary}[theorem]
\newtheorem*{remark}{Remark}
\newtheorem{definition}{Definition}
\newtheorem{example}{Example}
\renewcommand{\qedsymbol}{$\blacksquare$}

\newcommand{\cmpl}{\mathbb{C}}
\newcommand{\lieg}{\mathfrak{g}}
\newcommand{\lieh}{\mathfrak{h}}
\newcommand{\lies}{\mathfrak{s}}
\newcommand{\lien}{\mathfrak{n}}
\newcommand{\Ext}{\operatorname{Ext}}
\newcommand{\Hom}{\operatorname{Hom}}
\newcommand{\ad}{\operatorname{ad}}
\newcommand{\Tor}{\mathrm{Tor}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}

\newcommand{\lmod}[1]{\operatorname{\mathbf{#1-mod}}}
\newcommand{\rmod}[1]{\operatorname{\mathbf{mod-#1}}}

\setcounter{tocdepth}{2}
\setcounter{secnumdepth}{2}


\begin{document}
\maketitle

\begin{abstract}
    J. Taylor \cite{Taylor1970} introduced the notion of the joint spectrum of several commuting
    operators in Banach space and proved the existence of the holomorphic functional calculus in
    the neighbourhood of the spectrum. The natural question was, if it is possible to generalize
    the spectrum for tuples of not necceserily commuting operators. A.S. Fainshtein extended the
    notion of the Taylor spectrum to the tuples of operators, generating nilpotent Lie algebra. A
    bit later, E. Boasso and A. Larotonda defined it for solvable Lie algebras and proved the
    projection property. In 2010, A. Dosi proved a version of noncommutative holomorphic functional
    calculus for nilpotent Lie algebras.
    
    In the paper we generalize the notion of Taylor spectrum to modules over an arbitary Lie
    algebra and study it for finite-dimensional modules. We show, that in case of nilpotent and
    semisimple Lie algebras, the spectrum can be described as the set of simple submodules. We also
    show, that this result does not hold for solvable Lie algebras and give the precise description
    of the spectrum in case of the Borel subalgebra of semisimple Lie algebra.
\end{abstract}

\tableofcontents
\section{Introduction}%
\label{sec:introduction}
\input{introduction.tex}

\section{Preliminaries}%
\label{sec:preliminaries}
\input{preliminaries.tex}

\section{Taylor spectrum of \texorpdfstring{$\lieg$-module}{g-module}}%
\label{sec:spectrumofmodule}
\input{spectrumofmodule.tex}

\section{Case of semisimple Lie algebras}%
\label{sec:semisimple}
\input{semisimple.tex}

\section{Spectrum of one-dimensional extensions}%
\label{sec:1extensions}
\input{1extensions.tex}

\section{Case of solvable Lie algebras}%
\label{sec:solvable}
\input{solvable.tex}

%\section{Case of nilpotent Lie algebras}
%\label{sec:nilpotent}
%\input{nilpotent.tex}


%\section{Case of borel subalgebra of semisimple Lie algebra}
%\label{sec:borel}
%\input{borel.tex}
\printbibliography

\end{document}
